### 2017-10-22 TechnicalReport/article_3.tex
adding concepts and references

@@

\addcontentsline{toc}{section}{Acknowledgments} % Adds this section to the table of contents

@@

\bibitem{DISENO DE ALGORITMOS PARALELOS}
En el texto: (cs.buap, 2017)
Bibliografía: cs.buap. (2017). Diseño de algoritmos paralelos. [online] \href{https://www.cs.buap.mx/~mtovar/doc/ProgConc/ProgramacionParalela.pdf}{Available clicking here} [Accessed 21 Oct. 2017].

\bibitem cs.fit.edu. (2017). \textit{A Comparison of Document Clustering Techniques.} [online]  \href{http://cs.fit.edu/~pkc/classes/ml-internet/papers/steinbach00tr.pdf}{Available clicking here} [Accessed 18 Oct. 2017].

>>>>

	\item[Parallel computing] 
	Is a technique that consists of execute many calculations at the same time to solve big problems in less time than it could take in conventional computing. There are different kinds of parallel computing:
	“Instruction-level parallelism (ILP): Multiple instructions from the same instruction stream can be executed concurrently this kind is limited in practice by data and control dependences.
	Thread-level or task-level parallelism (TLP): Multiple threads or instruction sequences from the same application can be executed at the same time those could be generated by compiler/user and managed by compiler and hardware and is limited in practice by communication/synchronization overheads and by algorithm characteristics.
	Data-level parallelism (DLP): Instructions from a single stream operate concurrently on several data is limited by non-regular data manipulation patterns and by memory bandwidth 
	Transaction-level parallelism: Multiple threads/processes from different transactions can be executed concurrently and is limited by concurrency overheads”\cite{Parallel Computing}.
	\item[Domain Partition] “In this type of partitioning, the data associated with a problem is decomposed. Each parallel task then works on a portion of the data.” \cite{parallel_comp_lawrence_nat_lab}

	\item[MPI] 
	“MPI is a standardized and portable message-passing system. Message-passing systems are used especially on distributed machines with separate memory for executing parallel applications. With this system, each executing process will communicate and share its data with others by sending and receiving messages. MPI is the specification resulting from the MPI-Forum which involved several organizations designing a portable system (that can allow programs to work on a heterogeneous network).
	Since the data can only be shared by exchanging messages, this standard is not intended for use on shared-memory systems, like a multiprocessor computer. Basically, MPI includes point-to-point communication, collective communication (over a network of processes), process groups, bindings for Fortran and C and other advanced functions” \cite{MPI}

	\item[MPI Directives]
	Mpi directives are a set of collective communication routines and some variants:
	MPI\_Bcast
	“A broadcast is one of the standard collective communication techniques. During a broadcast, one process sends the same data to all processes in a communicator. One of the main uses of broadcasting is to send out user input to a parallel program, or send out configuration parameters to all processes.” \cite{mpi_bcast}.
	MPI\_Scatter 
	“Is a collective routine that is very similar to MPI\_Bcast. MPI\_Scatterinvolves a designated root process sending data to all processes in a communicator. The primary difference between MPI\_Bcast and MPI\_Scatteris that MPI\_Bcast sends the same piece of data to all processes while MPI\_Scatter sends chunks of an array to different processes.
	MPI\_Gather is the inverse of MPI\_Scatter. Instead of spreading elements from one process to many processes, MPI\_Gather takes elements from many processes and gathers them to one single process. This routine is highly useful to many parallel algorithms, such as parallel sorting and searching” \cite{mpi_directives}.

	\item[Overhead (computing)] “The amount of time required to coordinate parallel tasks, as opposed to doing useful work. Parallel overhead can include factors such as:
	- Task start-up time
	- Synchronizations
	- Data communications
	- Software overhead imposed by parallel languages, libraries, operating system, etc.
	- Task termination time”  \cite{parallel_comp_lawrence_nat_lab}

@@

@@

\bibitem{Parallel Computing}
Types of Parallelism. [online] \href{http://www.inf.ed.ac.uk/teaching/courses/pa/Notes/lecture02-types.pdf}{Available clicking here} [Accessed 22 Oct. 2017].

\bibitem{MPI}
En.wikibooks.org. (2017). Message-Passing Interface - Wikibooks, open books for an open world. [online] \href{https://en.wikibooks.org/wiki/Message-Passing_Interface}{Available clicking here} [Accessed 22 Oct. 2017].

\bibitem{mpi_bcast} 
Mpitutorial.com. (2017). MPI Broadcast and Collective Communication · MPI Tutorial. [online] \href{http://mpitutorial.com/tutorials/mpi-broadcast-and-collective-communication/}{Available clicking here} [Accessed 22 Oct. 2017].

\bibitem{mpi_directives} 
Mpitutorial.com. (2017). MPI Scatter, Gather, and Allgather · MPI Tutorial. [online] \href{
	http://mpitutorial.com/tutorials/mpi-scatter-gather-and-allgather/}{Available clicking here} [Accessed 22 Oct. 2017].

\bibitem{DISENO DE ALGORITMOS PARALELOS}
DISENO DE ALGORITMOS PARALELOS. cs.buap. (2017). [online] \href{https://www.cs.buap.mx/~mtovar/doc/ProgConc/ProgramacionParalela.pdf}{Available clicking here} [Accessed 21 Oct. 2017].
